We  obtained {\em Spitzer}/IRS spectral maps of 12 regions within M31 covering wavelengths 5--21~$\mu$m. 
The spectra from those regions, except for the nucleus, are similar to spectra obtained from other nearby  star-forming galaxies. 
Early  ISOCAM observations towards 4 regions of M31 showing a suppression 
of the 6--8~$\mu$m features' strength and an enhancement of  the 11.3~$\mu$m feature intensity and FWHM \citep{1998Cesarsky} were likely affected by the background subtraction methods applied.

We recover the well-known strong correlation between the 6.2/11.2 and 7.7/11.2 $\mu$m PAH intensity ratios that is governed by the PAH charge balance.  This is another indicator that the PAH emission in all regions but the nucleus is typical. The PAH EQWs in M31 regions show a decreasing trend with increasing radiation hardness, consistent with previous 
results from other nearby galaxies. The distribution of PAH EQWs with metallicity is well within the range of the starburst galaxy sample of \citet{Engelbracht_2008}. 
We did not have enough data from low-metallicity regions of M31 to observe the decreasing trend of EQWs at low metallicities which is visible in other galaxies.

Different spectral features (11.2~$\mu$m PAH emission, [NeIII] 15.5~$\mu$m line emission, silicate emission) show distinct spatial distributions in the nuclear region. Mid-infrared spectra from near the nucleus of M31 show either suppressed 6--8~$\mu$m features and a strong 11.3~$\mu$m feature
(15\arcsec off-nucleus) or silicate emission around 9.7~$\mu$m  (on-nucleus). The silicate emission profile is redshifted and broader than that observed towards the Galactic centre, in line with previous results from other galaxies and the M81 nucleus.  We contrast the spectral properties of the nuclei of M31 and M81 and find differences in the peak position and FWHM of the silicate feature, the silicate emitting region, the PAH emission, and the fine-structure line emission. 
The nuclear spectrum is similar to that of six other nearby galaxies known to have low luminosity AGN activity. This could strengthen the
suggestion by \citet{Smith:2007lr} that low $L(7.7\mu{\rm m})/L(11.3\mu{\rm m})$ is an indicator of low luminosity AGN. %,but this feature ratio could also be due to a lack of ionized PAHs. 
The nuclear silicate emission is another possible AGN indicator.
The 12~$\mu$m luminosity can be used to estimate a bolometric luminosity for the M31 nucleus of $1.6\times 10^{40}$~erg~s$^{-1}$,
well within the `low-luminosity' classification, but well above the value estimated from the X--ray flux.
